Factors affecting reliablity of state-space age-structured assessment models

### 2023-04-25 Project_0/paper/paper.Rmd
some text added to M-Ecov readme and some other code edits
saving work, fixing cor par setting in set_M.R

Standard deviation for log-aggregate catch was 0.1. There were two levels of observation error variance for indices and age composition for both indices and fleet catch. A low uncertainty specification assumed standard deviation of both series of log-aggregate index observations was 0.1 and the standard deviation of the logistic-normal for age composition observations was 0.3 In the high uncertainty specification the standard deviation for log-aggregate indices was 0.4 and that for the age composition observations was 1.5.

@@

>>>>

Standard deviation for log-aggregate catch was 0.1. There were two levels of observation error variance for indices and age composition for both indices and fleet catch. A low uncertainty specification assumed standard deviation of both series of log-aggregate index observations was 0.1 and the standard deviation of the logistic-normal for age composition observations was 0.3 In the high uncertainty specification the standard deviation for log-aggregate indices was 0.4 and that for the age composition observations was 1.5. For all estimating models, standard deviation for log-aggregate observations was assumed known whereas that for the logitic-normal age composition observations was estimated.

@@

\begin{table}
\caption{Distinguishing characteristics of the operating models with random effects on survival.}
{\input{naa_om_tab}}
\end{table}

\begin{table}
\caption{Distinguishing characteristics of the operating models with random effects on natural mortality.}
{\input{M_om_tab}}
\end{table}

\begin{table}
\caption{Distinguishing characteristics of the operating models with random effects on selectivity.}
{\input{Sel_om_tab}}
\end{table}

\begin{table}
\caption{Distinguishing characteristics of the operating models with random effects on catchability.}
{\input{q_om_tab}}
\end{table}
